Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-12-18 src/tf-cutcell-comparison/responses2.tex
remove discussion of CTCS sensitivity to terrain profile/domain width

\begin{quotation}
 Lines 271-279 and Table 1 – The $\ell_2$ error norms have changed by more than an order  of magnitude from those reported in the original manuscript. What changed?
\end{quotation}
In the first draft, the $\ell_2$ values had not been normalised, such that $\ell_2 = \sqrt{\sum_c \left(\phi - \phi_T\right)^2 \mathcal{V}_c}$.  This was fixed in the second draft so that $\ell_2$ was calculated correctly according to equation (13).
\begin{quotation}
 Lines 280-285 – Reviewer 2 questioned the large change in the $\ell_2$ error norm when 
 the domain width was changed from 301 to 300 km. I share the concern expressed 
 by this reviewer and find the authors' added explanation (``It's likely that changes in 
 the domain width affect the wave power spectrum of the discrete terrain profile.'') to 
 be inadequate. If the results are sensitive to the exact location of the lateral 
 boundaries, then the numerical experiment is not well designed; the boundaries 
 should be moved far enough away from the mountain so that this sensitivity 
 disappears.  Is it possible that the authors shifted the location of the terrain by a half 
 grid interval when they changed the domain width by one grid interval? This would 
 occur if they just defined the center of the terrain profile to be in the center of the 
 domain. If that’s the case, then the results are understandable since numerically, it's a 
 different terrain shape. However, the changing behavior would have nothing to do 
 with the domain width, and thus this sensitivity test should then be removed from 
 the paper altogether. One would get the same sensitivity leaving the domain width 
 fixed and just shifting the terrain location by one-half grid interval.  
\end{quotation}
Yes, the change in domain width causes the terrain to be shifted by $\Delta x / 2$, and it is this which results in a change in accuracy.  We had not intended to perform a sensitivity test, but only to clarify the specification for the \citet{schaer2002} advection test.  \TODO{update the manuscript to put less emphasis on this}

@@

\begin{quotation}
 Lines 364-368 – The authors did not need to run these resting atmosphere 
 simulations to reach the conclusion stated in this paragraph. As stated in my first 
 review, this test case does not challenge the numerics on a cut-cell grid since the horizontal pressure-gradient errors will obviously be reduced in the vicinity of the 
 low level inversion where the coordinates surfaces are perfectly horizontal. A better 
 test case might be to specify an inversion layer that intersects the terrain, since on 
 the cut-cell grid, it's only just adjacent to the terrain where pressure gradient 
 calculations between cell centers are not horizontal.   
\end{quotation}
\TODO{good idea, we should do this, but first see if anyone else does something similar (zaengl2012?).  Should we abandon the klemp2011 test entirely or just put less emphasis on its results?}

>>>>

\begin{quotation}
 Lines 271-279 and Table 1 – The $\ell_2$ error norms have changed by more than an order  of magnitude from those reported in the original manuscript. What changed?
\end{quotation}
In the first draft, the $\ell_2$ values had not been normalised, such that $\ell_2 = \sqrt{\sum_c \left(\phi - \phi_T\right)^2 \mathcal{V}_c}$.  This was fixed in the second draft so that $\ell_2$ was calculated correctly according to equation (13).
\begin{quotation}
 Lines 280-285 – Reviewer 2 questioned the large change in the $\ell_2$ error norm when 
 the domain width was changed from 301 to 300 km. I share the concern expressed 
 by this reviewer and find the authors' added explanation (``It's likely that changes in 
 the domain width affect the wave power spectrum of the discrete terrain profile.'') to 
 be inadequate. If the results are sensitive to the exact location of the lateral 
 boundaries, then the numerical experiment is not well designed; the boundaries 
 should be moved far enough away from the mountain so that this sensitivity 
 disappears.  Is it possible that the authors shifted the location of the terrain by a half 
 grid interval when they changed the domain width by one grid interval? This would 
 occur if they just defined the center of the terrain profile to be in the center of the 
 domain. If that’s the case, then the results are understandable since numerically, it's a 
 different terrain shape. However, the changing behavior would have nothing to do 
 with the domain width, and thus this sensitivity test should then be removed from 
 the paper altogether. One would get the same sensitivity leaving the domain width 
 fixed and just shifting the terrain location by one-half grid interval.  
\end{quotation}
Yes, the change in domain width causes the terrain to be shifted by $\Delta x / 2$, and it is this which results in a change in accuracy.  We had not intended to perform a sensitivity test, but only to clarify the specification for the \citet{schaer2002} advection test.

The paragraph discussing the sensitivity of CTCS to the change in mountain profile has been removed.  Line \TODO{xxx} clarifies the test setup required to reproduce \citet{schaer2002}'s results.

@@

\begin{quotation}
 Lines 364-368 – The authors did not need to run these resting atmosphere 
 simulations to reach the conclusion stated in this paragraph. As stated in my first 
 review, this test case does not challenge the numerics on a cut-cell grid since the horizontal pressure-gradient errors will obviously be reduced in the vicinity of the 
 low level inversion where the coordinates surfaces are perfectly horizontal. A better 
 test case might be to specify an inversion layer that intersects the terrain, since on 
 the cut-cell grid, it's only just adjacent to the terrain where pressure gradient 
 calculations between cell centers are not horizontal.   
\end{quotation}
\TODO{good idea.  zaengl2012 did something similar by raising the mountain to 4km, but we think that simply moving the inversion layer is preferable because the mesh remains constant.  Should we abandon the klemp2011 test entirely or just put less emphasis on its results?}

### 2015-12-18 src/tf-cutcell-comparison/tf-cutcell-comparison.tex
remove discussion of CTCS sensitivity to terrain profile/domain width

The domain is \SI{301}{\kilo\meter} wide and \SI{25}{\kilo\meter} high, discretized onto a grid with \(\Delta x = \SI{1}{\kilo\meter}\) and \(\Delta z^\star = \SI{500}{\meter}\).  The domain specified by \citet{schaer2002} is \SI{300}{\kilo\meter} between the outermost cell centres where tracer values are specified.  In order to reproduce the result from \citet{schaer2002}, the domain has been extended horizontally by \(\Delta x/2\) \si{\meter} in both directions so that the distance between the outermost cell centres is still \SI{300}{\kilo\meter}.

@@

\TODO{put less emphasis on this, just clarify the correct test setup to obtain Schaer's results.}
The centred linear scheme is sensitive to grid-scale changes in the terrain profile: when the domain width is reduced to \SI{300}{\kilo\meter}, the $\ell_2$ error on the BTF grid rises from \num{0.284} to \num{0.432}.  The same sensitivity is found using terrain following coordinates and centred differences in space and time, as implemented by \citet{schaer2002}.  The upwind-biased cubic scheme is less sensitive to the same change, with the $\ell_2$ error decreasing from \num{0.112} to \num{0.105}.  It is likely that changes in the domain width affect the wave power spectrum of the discrete terrain profile.  Grid-scale oscillations persist in the centred linear scheme but are damped by the upwind-biased scheme.

>>>>

The domain width is \SI{301}{\kilo\meter}, taken as the horizontal distance between the inlet and outlet boundaries.  The domain is \SI{25}{\kilo\meter} high, discretized onto a grid with \(\Delta x = \SI{1}{\kilo\meter}\) and \(\Delta z^\star = \SI{500}{\meter}\).  Note that \citet{schaer2002} measured the domain width as \SI{300}{\kilo\meter} between the outermost cell centres where tracer values are specified.  The two domain sizes are equivalent irrespective of the measure.

@@
